Refinements for Open Automata

### 2023-06-26 2021-Refinement/paper/refinementarticleV2.tex
small improvements

Before reasoning on the properties of simulation. we need to introduce one additional notion that characterises when the composition of two automata does not introduce new blocked transitions.

>>>>

Before reasoning on the properties of simulation, we need to introduce one additional notion that characterises when the composition of two automata does not introduce new blocked transitions.
